---
title: "STA 4320 Homework 3"
author: "John Doe"
date: "9/26/18"
output: html_document
---

# Question 4 ISLR 3.7.8


## Solution.

### Part (a)
The following was done after installing package "ISLR" from the console with the following code:
install.packages('ISLR')

```{r}
library(ISLR)
head(Auto)
```
```{r}
lm.fit=lm(mpg~horsepower,data=Auto)
attach(Auto)
summary(lm.fit)
```


#### (i)
Going by the Estimate column and horsepower row, we see that mpg and horsepower have a relationship, with an estimated coefficient of -0.157845.

#### (ii)
The coefficient between horsepower and mpg has a p-value less than the level of significance alpha = 2e-16, making the relationship strong enough to be considered significant.

#### (iii)
The relationship between mpg and horsepower is negative

#### (iv)
According to the formula constructed from the estimates of the intercept and slope, a horsepower of 98 can expect an estimated mpg of 24.467051
```{r}
confint(lm.fit)
```
Using the confidence intervals, we may expect an mpg ranging from 21.814546 to 27.1196053.

### Part (b)

```{r}
plot(horsepower,mpg)
abline(lm.fit)
```


### Part (c)

```{r}
par(mfrow=c(2,2))
plot(lm.fit)
```


Some of the diagnostic plots show nonlinear relationships. The lines include Residuals vs. Leverage, Residuals vs. Fitted values, and Fitted values versus the square root of the standardized residuals


# Question 5


## Solution.

### Part (a)

```{r}
epsilon <- rnorm(50)
```


### Part (b)


```{r}
X <- seq(0,5,length = 50)
```


### Part (c)

```{r}
Y <- 5 + 2*X + epsilon
```


### Part (d)

```{r}
lm.fit <- lm(Y~X)
plot(X,Y)
abline(lm.fit)
y <- 5 + 2*X
lines(y, col = "red")

```


### Part (e)

```{r}
eps <- rnorm(50)
x <- seq(0,5,length = 50)
y <- 4 + 3*x + eps
y1 <- 4 + 3*x
lm.fit1 <- lm(y~x)
plot(x,y)
abline(lm.fit1)
lines(y1, col = "blue")

```


### Part (f)

```{r}
eps1 <- rnorm(50, sd=3)
x <- seq(0,5,length = 50)
y <- 2 + 2*x + eps
y1 <- 2 + 2*x
lm.fit1 <- lm(y~x)
plot(x,y)
abline(lm.fit1)
lines(y1, col = "green")
```


After making a new graph with a wider variance of 9, there is now a wider spread of values away from the linear model.