---
title: "STA 4320 Homework 4"
author: "Eric Muro"
date: "10/3/18"
output: html_document
---

# Question 4 ISLR 3.7.10


## Solution.

### Part (a)

```{r}
library(ISLR)
head(Carseats)
```

```{r}
data("Carseats")
lm.fit <- lm(Sales~Price+Urban+US, data=Carseats)
summary(lm.fit)
```


### Part (b)

Looking at the negative coefficient for the variable Price, it appears that allowing the price company to charge for car seats at each site will have an inverse relationship with car seat sales. Also, looking at the coefficient for the qualitative variable UrbanYes, we see that vendors located in urban areas struggle to sell child car seats. The last coefficient, USYes, has a positive coefficient, suggesting that vendors located in the United States sell more child car seats.

### Part (c)

$y = 13.043469 - 0.054459(X_1) - 0.021916(X_2) + 1.200573(X_3) + epsilon$
Where $X_1=1$ if the price company charges for car seats, and $X_1=0$ if not,
$X_2=1$ if the car seat vendor is located at an urban area and $X_2=0$ if the vendor is located in a rural area, and $X_3=1$ if the vendor is located within the U.S. and $X_3=0$ if located outside the U.S.. $epsilon$ represents the error from mistakes

### Part (d)

We can reject the null hypothesis for the Price and US variables, as the p-values are very small and therefore significant.

### Part (e)

```{r}
lm.fit2 <- lm(Sales ~ Price+US, data=Carseats)
summary(lm.fit2)
```


### Part (f)

We note that the Adjusted R-squared value in (e), 0.2354, is slightly larger that the value in (a), which is at 0.2335. This implies that the linear model in (e) fits slightly better than (a).

### Part (g)

```{r}
confint(lm.fit2)
```


# Question 5


## Solution.

```{r}
data("Auto")
```


### Part (a)

```{r}
fit1 <- lm(mpg~cylinders, data=Auto)
summary(fit1)$adj.r.squared

fit2 <- lm(mpg~displacement, data=Auto)
summary(fit2)$adj.r.squared

fit3 <- lm(mpg~horsepower, data=Auto)
summary(fit3)$adj.r.squared

fit4 <- lm(mpg~weight, data=Auto)
summary(fit4)$adj.r.squared

fit5 <- lm(mpg~acceleration, data=Auto)
summary(fit5)$adj.r.squared

fit6 <- lm(mpg~year, data=Auto)
summary(fit6)$adj.r.squared

fit7 <- lm(mpg~origin, data=Auto)
summary(fit7)$adj.r.squared
```

```{r}
summary(lm(mpg~weight+cylinders, data=Auto))$adj.r.squared

summary(lm(mpg~weight+displacement, data=Auto))$adj.r.squared

summary(lm(mpg~weight+horsepower, data=Auto))$adj.r.squared

summary(lm(mpg~weight+acceleration, data=Auto))$adj.r.squared

summary(lm(mpg~weight+year, data=Auto))$adj.r.squared

summary(lm(mpg~weight+origin, data=Auto))$adj.r.squared
```

```{r}
summary(lm(mpg~weight+year+cylinders,data=Auto))$adj.r.squared

summary(lm(mpg~weight+year+displacement,data=Auto))$adj.r.squared

summary(lm(mpg~weight+year+horsepower,data=Auto))$adj.r.squared

summary(lm(mpg~weight+year+acceleration,data=Auto))$adj.r.squared

summary(lm(mpg~weight+year+origin,data=Auto))$adj.r.squared
```

```{r}
summary(lm(mpg~weight+year+origin+cylinders,data=Auto))$adj.r.squared

summary(lm(mpg~weight+year+origin+displacement,data=Auto))$adj.r.squared

summary(lm(mpg~weight+year+origin+horsepower,data=Auto))$adj.r.squared

summary(lm(mpg~weight+year+origin+acceleration,data=Auto))$adj.r.squared
```

```{r}
summary(lm(mpg~weight+year+origin+displacement+cylinders,data=Auto))$adj.r.squared

summary(lm(mpg~weight+year+origin+displacement+horsepower,data=Auto))$adj.r.squared

summary(lm(mpg~weight+year+origin+displacement+acceleration,data=Auto))$adj.r.squared
```

```{r}
summary(lm(mpg~weight+year+origin+displacement+horsepower+cylinders,data=Auto))$adj.r.squared

summary(lm(mpg~weight+year+origin+displacement+horsepower+acceleration,data=Auto))$adj.r.squared
```

```{r}
summary(lm(mpg~weight+year+origin+displacement+horsepower+cylinders+acceleration,data=Auto))$adj.r.squared
```


### Part (b)


```{r}
summary(lm(mpg~cylinders+displacement+horsepower+weight+acceleration+year+origin,data=Auto))
```

```{r}
summary(lm(mpg~displacement+weight+year+origin,data=Auto))
```

```{r}
summary(lm(mpg~weight+year+origin,data=Auto))
```

From what we have observed attempting backward selection using Adjusted R-Squared values, the predictive model for mpg using all predictors (cylinders, displacement, horsepower, weight, acceleration, year, and origin), is the model with the best fit, at an adjusted R-Squared value of 0.8182.

